The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2018-12-06 Ben_Manuscripts/transport/Outline.tex
Calculating coordination number
Updates

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  A continuous time random walk (CTRW) is a stochastic process characterized by a 
  distribution of hop lengths and dwell times.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item Incorporates effects of `aging' since it samples long dwell times
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution while the distribution of dwell
	times fits relatively well to an exponential distribution characteristic of a
	Poisson process. (See supporting information)
  \end{itemize}

  \begin{equation}
	Ae^{-x}
  \end{equation}

  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
  magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed trajectories by generating sequences of dwell times 
        and hop lengths randomly sampled from our fit distributions.
	\item For time scales much greater than the characteristic time of our
	exponential dwell time distribution, solutes exhibit Brownian motion. 
	\item The MSD curve becomes linear
	\item We fit a line to the MSD curve and used the Einstein relationship
	to relate its slope to the macroscopic diffusion coefficient.
	\item We found convergence of the value of the diffusion coefficient 
	calculated in this way afer x steps (See Supporting Information)
  \end{itemize}

@@

@@

  \subsection{Macroscopoic Diffusion Coefficients}

  \subsection{Simulated Predictions}\label{section:D_macro}

  Polar molecules generally exhibit a hop diffusion mechanism. 
  \begin{itemize}
	\item Each trajectory is characterized by an exponential distribution of
	dwell times between hops of random lengths from a Gaussian distribution.
  \end{itemize}

  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
  trajectories and predicted macroscopic diffusion coefficients which are
  presented in Table TBD.

@@

@@

  \subsection{Experimental Measurements}

@@

  In order to truly understand the molecular origins of the macroscopic
  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
  microscopic interactions between solutes and the membrane that lead to the
  observed dwell time and hop distributions.
  \begin{itemize}
	\item We studied the radial distribution functions of solutes as a
	function of distance from the pore center
	\item We looked at hydrogen bonding patterns
	\item Order parameters
  \end{itemize}

>>>>

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
  process characterized by a distribution of hop lengths and dwell times.
  \begin{itemize}
	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
	and random walks on a fractal.
	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
  \end{itemize}

  We fit our data to a CTRW model by using our data in order to construct 
  dwell time and hop length distributions.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item Incorporates effects of `aging' since it samples long dwell times
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution 
	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
  \end{itemize}

  \begin{equation}
	Ax^{(-1 - \alpha)}
  \end{equation}

  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
  magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed trajectories by generating sequences of dwell times 
        and hop lengths randomly sampled from our fit distributions.
	\item For time scales much greater than the characteristic time of our
	dwell time distribution, solutes exhibit Brownian motion. 
	\item The MSD curve becomes linear
	\item We fit a line to the MSD curve and used the Einstein relationship
	to relate its slope to the macroscopic diffusion coefficient.
	\item We found convergence of the value of the diffusion coefficient 
	calculated in this way afer x steps (See Supporting Information)
  \end{itemize}

@@

  \subsubsection*{Coordination number}

  We quantified the coordination of solutes with surrounding molecules and
  functional groups in two ways.
  \begin{itemize}
	\item By counting the number of coordinated molecules to a given solute
	based on a distance cut-off. Gives frame-by-frame information. 
	\item By averaging 3D spherical radial distribution function calculated for
	each solute.
  \end{itemize}

@@

  \subsection{Macroscopic Diffusion Coefficients}

  \subsubsection{Simulated Predictions}\label{section:D_macro}

  Polar molecules generally exhibit a hop diffusion mechanism. 
  \begin{itemize}
	\item Each trajectory is characterized by a power law distribution of
	dwell times between hops of random lengths from a Gaussian distribution.
  \end{itemize}

@@

  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
  trajectories and predicted macroscopic diffusion coefficients which are
  presented in Table TBD.
  \begin{itemize}
	\item We confirmed that our molecules exhibit anomalous diffusion
	by fitting a power law to the MSD curve. The exponent is less than
	1, indicative of anomalous subdiffusion.
	\item We used the decision making process given by Meroz and Sokolov
	in order to identify the appropriate subdiffusion model to use 
	based on our time series (See Section S-TBD of the Supporting info for
	more details).
	\item The motion of the solutes is non-ergodic and the steps are
	uncorrelated which tells us the system is likely well-described
	by a CTRW. 
  \end{itemize}

@@

  Solutes in systems with lower water content exhibit lower diffusion coefficients.
  \begin{itemize}
	\item Pores are more crowded when there is less water (show RDFs of each)
	\item Not a linear function of pore size - radius increase by x, D increases by y
	\item Larger influence on bigger molecules
  \end{itemize}

  \subsubsection{Experimental Measurements}

@@

  In order to truly understand the molecular origins of the macroscopic
  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
  microscopic interactions between solutes and the membrane that lead to the
  observed dwell time and hop distributions.
  \begin{itemize}
	\item We studied the radial distribution functions of solutes as a
	function of distance from the pore center
	\item We looked at hydrogen bonding patterns
	\item Coordination numbers
	\item Order parameters
  \end{itemize}
